Predicting sales of newly published books

### 2015-10-13 paper.tex
removing the old text related to the variable selection process

In general, historical data is used to make time series, and from them extracting 
common patterns and obtaining accurate predictions.
However, in the case of new products, such as the issue of new books, past patterns 
is difficult to observe as there is no available historical sales data \cite{ChingChin2010}.

@@

Thus, from the initial set of variables, the SOM \cite{kohonen1998} was applied 
in order to reduce the dimensionality of the input data and to choose an 
appropriate set of variables.

@@

As stated in Section \ref{sec:problem}, an expert sales manager collaborated in 
this research in the stage of data analysis. Thus, the process was as follows:
\begin{itemize}
  \item First, the expert removed superfluous variables, and dimensionality was 
  reduced from 50 to 43 inputs.
  \item Then, the expert, using his knowledge and the information obtained 
  analyzing the SOM results, removed some inputs, reducing the number of 
  variables describing a book from 43 to 13.
  \item The company asked to include the information about \emph{editorial} 
  and \emph{materia}. Thus, in a new iteration, taking into account the expert's %FERGU: materia no existe en inglés. Subject?
  advice and the information obtained analyzing the SOM results, the number of 
  inputs was decreased to 7.
  \item In a third step, several forecasting methods were used on the obtained 
  dataset, and the best was chosen to obtain an accurate predicting model.
  \item Finally, some information about the new book, such as \emph{author}, 
  although not included in the obtained models, was taken into account by 
  the expert sales manager to modify the forecasted results. 
\end{itemize}

  %  
  %  El proceso que seguimos, resumido para el paper, es:
  %  
  %  [43 entradas] en 2013-01 vamos a tomar 
  %  	pb_noneg.csv para obtener pb_ventas.csv (es el pb_ventas.arff)
  %  	y hacer el SOM
  %  
  %  [13 entradas] en 2013-02-08 vamos a tomar 
  %  	controlado_reducido.csv.arff (197 líneas)
  %  	pbenero.csv.arff (5656 líneas)
  %  	y hacer el SOM
  %  
  %  [7 entradas; materia editorial] en 2013-02-25 vamos a tomar
  %  	pbRAWtrn.arff
  %  	pbRAWtst.arff
  %

More specifically, in a first step, the expert analyzed the 50 input variables 
describing each book to remove those that were superfluous.
Table \ref{tabla:params43} shows the set of variables describing a book 
(43 total inputs) that the expert manager determined as non-superfluous or 
non-redundant.

\begin{table}[!h]
\caption{Variables describing a book (43 total inputs), after the expert 
manager analized the original dataset provided by the company Trevenque to 
remove some inputs.}
\label{tabla:params43}
\begin{center}
\begin{tabular}{|c|c|}
\hline

\begin{minipage}{2.3in} \begin{verbatim}
DEPARTMENT STORES POINTS OF SALE FIRST YEAR
REST OF SALES FIRST YEAR
NEGATIVE SALES ENVIRONMENT
DISTRIBUTED THROUGH DEPARTMENT STORES FIRST YEAR
TOTAL RETURNS
REPRINTS
MALL SALES FIRST YEAR
TOTAL POINTS OF SALE FIRST YEAR
UNITS DISTRIBUTED AS NOVELTY
PRINT-RUN
NUMBER OF REPRINTS
RETURNS - DEPARTMENT STORES
REST OF POINTS OF SALE FIRST YEAR
REST OF SALES
DELEGATES POINTS OF SALE
REST OF RETURNS
DELEGATES POINTS OF SALE FIRST YEAR
POSITIVE SALES ENVIRONMENT
REST OF DISTRIBUTED FIRST YEAR
REST OF POINTS OF SALE
TOTAL RETURNS FIRT YEAR
DELEGATES RETURNS
\end{verbatim} \end{minipage}     &

\begin{minipage}{2.3in} \begin{verbatim}
DEPARTMENT STORES SALES
TOTAL DISTRIBUTED FIRST YEAR
TOTAL POINTS OF SALE
DISTRIBUTED THROUGH DEPARTMENT STORES
DISTRIBUTED THROUGH DELEGATES FIRST YEAR
POINTS OF SALE - DEPARTMENT STORES
TOTAL SALES FIRST YEAR
MEDIUM SALES ENVIRONMENT
WEEKS FOR SALE
DISTRIBUTED THROUGH DELEGATES
AUTHOR
DELEGATES SALES FIRST YEAR
GIFTS
RETURNS -  DEPARTMENT STORES  FIRST YEAR
SALES THROUGH DELEGATES
DISTRIBUTED - REST
DELEGATES RETURNS FIRST YEAR
TOTAL DISTRIBUTED
REST OF RETURNS FIRST YEAR
RETAIL PRICER
TOTAL SALES (output)
\end{verbatim} \end{minipage}    \\

\hline
\end{tabular}
\end{center}
\end{table}
%FERGU: para ahorrar espacio se puede hacer la tabla inversa: variables que se han quitado (las 7)
%[pedro] no entiendo muy bien a qué te refieres...

Then, after analyzing the original dataset using the SOM to select the best %FERGU: parametros o framework SOM usados?
variables to be considered, and taking into account the knowledge of the company 
experienced manager, 13 inputs were considered. 
Figure \ref{fig:som43} shows the initial analysis of dataset using the total 
of 43 descriptive inputs per book.
Table \ref{tabla:params13} shows the set of variables describing a book after 
the second analysis.
	% esta gráfica no aporta nada, ni la siguiente tampoco. No se puede
	% colocar en un trabajo en revista  cómo ha ido el entrenamiento, sino
	% datos serios de análisis estadístico de las variables. 
	% [Pedro] sí, estoy de acuerdo. Esto va con el ISSUE #6
\begin{figure}[!h] 
\begin{center}
\begin{tabular}{c}
  \epsfig{file=som43vars.eps,width=11cm} \\
  \epsfig{file=som43umatrix.eps,width=5cm}
\end{tabular}
\caption{\small{Initial data analysis, using 43 descriptive variables per book, %FERGU: la figura está en español, pero ya lo sabréis :P
using SOM.}}
	% Cojollos, ¿qué trabajo os cuesta poner esto en inglés directamente? - JJ
	% [Pedro] sí, si estoy de acuerdo... hay días que me "sale" el texto en inglés,
	% pero hay días que soltar la parrafada en español me resulta más fácil    :/
        % Sería más bien exploratory data analysis o data visualization. 
        % Un gráfico no es un análisis. Y pon las cosas cortas en inglés, hombre - JJ
\label{fig:som43}
\end{center}
\end{figure}

\begin{table}[!h]
\caption{Variables that describe every book, 13 in total, after the
  second analysis carried out using the SOM along with the company
  experienced manager % él no hizo el análisis. No cuela con ``along with'' - JJ
to select the best variables to be considered to
  solve the sales forecasting problem.} 
\label{tabla:params13}
\begin{center}
\begin{tabular}{|c|}
\hline

\begin{minipage}{2.3in} \begin{verbatim}
TOTAL RETURNS
REPRINTS
TOTAL POINTS OF SALE FIRST YEAR
UNITS DISTRIBUTED AS NOVELTY
NUMBER OF REPRINTS
TOTAL RETURNS FIRT YEAR
TOTAL DISTRIBUTED FIRST YEAR
TOTAL POINTS OF SALE
WEEKS FOR SALE
TOTAL DISTRIBUTED
RETAIL PRICER
PRINT-RUN
TOTAL SALES (output)
\end{verbatim} \end{minipage}     \\

Finally, after analyzing the dataset with 13 descriptive inputs per %FERGU: describis los resultados antes de explicar que volveis a hacer SOM
book, and paying attention to the company experienced manager's
recommendations, 7 inputs were considered; specifically, variables
\emph{EDITORIAL} and \emph{SUBJECT} were included, while %FERGU: vale, no useis SUBJECT, usad mejor SUBJECT (SUBJECT es materia de física, creo xD).    ok, ¡gracias!
\emph{TOTAL DEVOLUTIONS, REPRINTS, TOTAL SELLING POINTS FIRST YEAR,
  NUMBER OF REPRINTS, TOTAL DEVOLUTIONS FIRT YEAR, TOTAL DISTRIBUTED FIRST YEAR,
  WEEKS FOR SALE, PRINT-RUN} were discarded.  
	% Hay que aportar datos de por qué se hizo esto. ¿Análisis de planos?
	% ¿Análisis de varianza? - jj
	% [Pedro] En cuanto estén los SOM definitivos lo añadimos. Está relacionado con el ISSUE #6
Figure \ref{fig:som13} shows the initial analysis of dataset using the SOM on 
the total of 13 descriptive inputs per book.
This, along with the expert manager knowledge determined the final 7 inputs 
to be considered.
Table \ref{tabla:params7} shows the final set of variables describing a book, 
taking into account the company experienced manager knowledge.

\begin{figure}[!h] 
\begin{center}
\begin{tabular}{c}
  \epsfig{file=som13vars.eps,width=11cm} \\
  \epsfig{file=som13umatrix.eps,width=5cm}
\end{tabular}
\caption{\small{Analysis of the initial data, using 13 descriptive variables per book, using the SOM.}} % Análisis de los datos iniciales, usando 13 variables descriptivas por libro, utilizando el SOM.}} %FERGU: teniais esto en español, lo he traducido al inglés :)
% describir de forma más precisa: visualización usando UMatrix de... - JJ
% ¡y usar nombres en inglés para las variables! - JJ
%[pedro] es el siguiente arreglo que le haré mañana al paper    ;)
\label{fig:som13}
\end{center}
\end{figure}

\begin{table}[!h]
\caption{Final set of variables describing a book, taking into account the company 
experienced manager knowledge, to be considered to solve the sales forecasting problem.}
\label{tabla:params7}
\begin{center}
\begin{tabular}{|c|}
\hline

\begin{minipage}{2.3in} \begin{verbatim}
UNITS DISTRIBUTED IN FIRST EDITION
TOTAL SELLING POINTS
TOTAL DISTRIBUTED
RETAIL PRICE
SUBJECT
EDITORIAL
TOTAL SALES (output)
\end{verbatim} \end{minipage}     \\

>>>>

In general, historical data is used to make time series, and from them extracting 
common patterns and obtaining accurate predictions.
However, in the case of new products, such as the issue of new books, past patterns 
is difficult to observe as there is no available historical sales data 
\cite{ChingChin2010} (only pre-sales data is available in this problem).

@@

Moreover, the algorithm runing times grow with the number of features, and thus 
making the algorithm impractical for problems with a large number of features 
\cite{Selvakuberan2008}. Feature selection task is usually carried out by 
searching through all possible combinations of features, evaluating each one.

During the evaluation, the set of all possible features is analyzed in order 
to find the best set of features, ranking them according to some metric.
In this process, the feature's predictive ability along with the degree 
of redundancy between them is considered.

Thus, in order to reduce the dimensionality of the input data and to choose an 
appropriate set of variables, both the SOM \cite{kohonen1998} method and several 
feature selection methods have been applied.

@@

As far as the feature selection methods are concerned, both a correlation-based 
feature subset evaluation method (CfsSubsetEval) \cite{Hall1998} and an 
adaptation of relief for attribute estimation (ReliefFAttributeEval) evaluation 
method \cite{RobnikSikonja1997} are used with two search criteria: BestFirst, 
that searches the space of feature subsets by greedy hill-climbing augmented 
with a backtracking facility, and Ranker, that ranks features by their individual 
evaluations.
